%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[document]{ragged2e}
\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\setlength{\footskip}{4.5pt}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\huge\textsc{Pedro Primor}} \\ \vspace{1pt}
    \ \href{mailto:hello@primor.me}{\faEnvelope \hspace{1pt} hello@primor.me}
    % $|$ \faLink \ \href{https://primor.me/}{\underline{primor.me}}
    $|$ \href{https://www.linkedin.com/in/primor/}{\faLinkedin/primor}
    $|$ \href{https://github.com/pprimor}{\faGithub/pprimor}
\end{center}

\section{About me}
    \justifying

Software Engineer at \href{https://pageproof.com/}{PageProof}, building cross-platform integrations that connect creative tools---including Canva, Microsoft Office, Adobe Creative Suite, and Final Cut Pro---with PageProof's review workflow. I design and ship user-focused solutions with \textbf{React, TypeScript, Swift, and Electron} across web, desktop, and mobile. \textbf{Languages:} Portuguese (native); English (full professional proficiency).

%-----------EXPERIENCE-----------
\section{Work experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Mar. 2023 -- Present}
      {PageProof.com Limited}{Remote}
        \resumeItemListStart
            \resumeItem{Building the \textbf{Jira} integration (proof references, synced issue comments, and approved-file attachment) using React, TypeScript, and Node.js.}
            \resumeItem{Developed a \textbf{QuarkXPress XTension} using React, TypeScript, and C++ for native QuarkXPress API integration, extending PageProof's review capabilities to QuarkXPress users.}
            \resumeItem{Developed a company-wide \textbf{OAuth 2.0} (\href{https://www.rfc-editor.org/rfc/rfc6749.html}{RFC 6749}) Authorization Server with \textbf{OpenID Connect (OIDC)} (\href{https://openid.net/connect/}{OpenID Connect}) support using \textbf{Node.js}, and enhanced cross-platform desktop capabilities with \textbf{Electron} and \textbf{Node.js}.}
            \resumeItem{Built product integrations for \textbf{Canva}, \textbf{Microsoft Office}, \textbf{Final Cut Pro}, and \textbf{Adobe UXP} (Photoshop/InDesign) using React, TypeScript, Swift, and platform SDKs.}
            \resumeItem{Improved the \textbf{PageProof web app} mobile user experience and UI responsiveness.}

        \resumeItemListEnd
        

    \resumeSubheading
      {Operations Research Analyst}{Jan. 2022 -- Sep. 2022}
      {CTT – Correios de Portugal, S.A.}{Lisbon, Portugal}
        \resumeItemListStart
            \resumeItem{Led an operations research and data analytics project optimizing \textbf{last-mile delivery} within the postal distribution network.}
            \resumeItem{Modeled and solved a \textbf{vehicle routing problem (VRP)} for postal delivery constraints and developed \textbf{Tableau} visualizations to support operational planning.}

            \resumeItemListEnd
  
    \resumeSubheading
      {Front-end Developer Intern}{Apr. 2020 -- Jul. 2020}
      {Altitude Software}{Lisbon, Portugal}
        \resumeItemListStart
            \resumeItem{Rebuilt legacy ASP.NET components using \textbf{React}, modernizing the user interface of a contact center management platform and improving maintainability.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {NOVA University Lisbon}{Sep. 2020 -- Dec. 2022}
    {Master of Science in Computer Science}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{\textit{Relevant coursework:} Artificial Intelligence, Concurrency and Parallelism, Data Modelling, Information Retrieval, Machine Learning}
      \resumeItemListEnd

  \resumeSubheading
    {Technische Universität Dresden}{Apr. 2021 -- Oct. 2021}
    {Erasmus+ Programme Mobility in Computer Science}{Dresden, Germany}

  \resumeSubheading
    {NOVA University Lisbon}{Sep. 2017 -- Sep. 2020}
    {Bachelor of Science in Computer Science}{Lisbon, Portugal}
      \resumeItemListStart
        \resumeItem{\textit{Relevant coursework:} Algorithms and Data Structures, Object-Oriented Programming, Databases, Sensors and Image Processing}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}